\section{Distributed Resolver Agent Installation and Configuration}\label{sec:resolver-agent}

\subsection{Overview}

The distributed resolver agent is a service intended to run in a build environment that
matches the build environment generally used for the code.  The service executes
the \scaresolver when events are handled by \cxoneflow that would invoke a scan.
The \scaresolver is typically executed in the code's build pipeline as a pre-step
for a multi-engine \cxone scan that includes an SCA scan.

The keys to a successful \scaresolver scan are generally:

\begin{itemize}
  \item The build tools used to obtain the dependency tree are the same versions and
    configurations as those used to build the code.
  \item The execution happens behind the enterprise firewall to allow for transitive
    dependency resolution of packages that are hosted in a private package repository.
\end{itemize}


\subsection{Installation and Configuration Pre-Requisites}

To install the distributed resolver agent, the following is required:

\begin{itemize}
  \item The distributed resolver agent installer appropriate for your target platform.
  \item An external message queue used by \cxoneflow and the distributed resolver agent (see Section \ref{sec:external-mq} for more details).
  \item A set of message queue credentials used by the distributed resolver agent (see Section \ref{sec:agent-mq-auth-req} for more details).
  \item A public key that is matched with a private key configured for use by the \cxoneflow server (see Section \ref{ref:server-key-pair} for more details).
  \item \scaresolver must be installed if intending to execute \scaresolver without a container.
  \item If intending to execute \scaresolver in a container:
  \begin{itemize}
    \item The system must have docker installed.
    \item The \toolkit build environment must be installed.
  \end{itemize}
\end{itemize}


\subsubsection{Message Queue Authorization}\label{sec:agent-mq-auth-req}

Distributed resolver agents communicate with \cxoneflow using an AMQP message queue. Each distributed
resolver agent must have a set of message queue credentials that limit how it can interact
with the message queue as appropriate for the agent's configured tags.

Table \ref{tab:agent-mq-user-perms} shows the permissions needed for the distributed resolver agent
to interact with the message queues.  Using a regular expression of "\texttt{\^{}cx:res:.*}" will allow
the agent to respond to events for any tag.  It is possible to limit which tags an agent can consume
by adding regular expressions that specify one or more tags at the end of the queue name.  For example, the
regular expression "\texttt{\^{}cx:res:.*(general|java-gradle)\$}" will limit the distributed resolver agent
to handling only tags \texttt{general} and \texttt{java-gradle}.

\begin{table}[ht]
  \caption{RabbitMQ User Permissions for the Distributed Resolver Agent}  
  \label{tab:agent-mq-user-perms}      
  \begin{tabularx}{\textwidth}{lcl}
      \toprule
      \textbf{Permission} & \textbf{Regular Expression} \\
      \midrule
      \texttt{Configure} & blank \\
      \midrule
      \texttt{Write} & \texttt{\^{}cx:res:.*} \\
      \midrule
      \texttt{Read} & \texttt{\^{}cx:res:.*} \\
      \midrule
      \bottomrule
  \end{tabularx}
\end{table}

Table \ref{tab:agent-mq-topic-perms} shows the topic permissions that limit the distributed resolver agent
to submitting messages with topics for scan completion.  Using the regular expression\\"\texttt{\^{}.exec.sca-resolver.scan-complete.*}"
allows the agent to post scan results for any agent.

To limit the agent to submitting messages with only the topics for tags the agent supports, the regular expression can
be modified to include the tags.  For example, the topic regular expression
"\texttt{\^{}.exec.sca-resolver.scan-complete.(general|java-gradle)\$}" will limit the agent to submitting
scan results for the tags \texttt{general} and \texttt{java-gradle}.

\begin{table}[ht]
  \caption{RabbitMQ User Topic Permissions for the Distributed Resolver Agent}  
  \label{tab:agent-mq-topic-perms}      
  \begin{tabularx}{\textwidth}{lcl}
      \toprule
      \textbf{Exchange} & \textbf{Permission} & \textbf{Regular Expression} \\
      \midrule
      \texttt{cx:res:SCA Resolver Scan In} & \texttt{Write} & \texttt{\^{}.exec.sca-resolver.scan-complete.*}\\
      \midrule
      \texttt{cx:res:SCA Resolver Scan In} & \texttt{Read} & blank \\
      \midrule
      \bottomrule
  \end{tabularx}
\end{table}

\subsubsection{Distributed Resolver Agent Deployment Considerations}

The \cxoneflow scan workflow that delegates resolver scans to distributed resolver agents
assumes that one or more agents are available to handle the delegated scan request. Any number
of distributed resolver agents that handle the same tag can be deployed.  It is suggested that
deployment of distributed resolver agents considers that resolver scans will fail in the event
that no distributed resolver agents are available to handle scan requests for one or more
tags.


\subsection{Security Considerations}\label{sec:resolver-agent-security}

As briefly described in Section \ref{sec:dist-resolver-security-considerations}, executing
part of a code build to extract a dependency tree can pose some risks. For example,
tools like Gradle define the build definition in the programming language Groovy; this Groovy
code executes when Gradle loads the build definition.  Other tools even execute scripts defined
in the dependency package leading to the popular method of "typo-squatting" as a means to
perform a remote-code-execution (RCE) attack directly on unsuspecting developers.  Executing an
untrusted build definition or loading a dependency containing malware into a build system is
a risk that comes from using open-source software.

Since the risk of malicious builds is always possible, the deployment of the distributed resolver agent
can be configured to mitigate these risks.  The section for each platform's install makes specific
recommendations for a secure deployment of the distributed resolver agent.  The general recommendations
for all platform deployments are:

\begin{itemize}
  \item \textbf{Assume that anyone with administrative access to a server with a distributed resolver agent installed
    can intercept all secrets configured on the \cxoneflow server.}
  \item It is a best practice to not allow developers administrative control over the configuration and
    execution of the distributed resolver agent.
  \item Utilize file permissions on the secret values used by the agent to limit which running processes
    can read the contents of the secrets
  \item Use the recommended file system permissions for each platform's deployment.
  \item Find a logical grouping of agents for message queue credential assignment to better avoid
    impact if any credentials are misused.
  \item Use the message queue account security settings to limit message queue access to agents such that they are only
    able to receive and send events required for their specific operations.
  \item If the agent is invoking \scaresolver as a shell execution, utilize a "run-as" configuration to
    run the resolver as a low-privilege account.
  \item Utilize the \scaresolver docker execution capability to sandbox the dependency resolution in a container.
  \item Avoid configuring a distributed resolver agent instance to execute \scaresolver for both shell and container dependency resolution
    unless proper precautions have been taken to avoid privilege escalation exploits through the container file system overlay.
\end{itemize}



\subsubsection{Installing on Debian Linux}

The installation on Debian Linux platforms uses the distributed resolver agent Debian installer package
found with the \cxoneflow release.  The installer performs the following steps:

\begin{itemize}
  \item The agent is installed at the path \texttt{/opt/cxoneflow-resolver-agent}
  \item The agent uses the configuration file \texttt{/etc/cxoneflow-resolver-agent/config.yaml}
  \item A config template is installed at \texttt{/etc/cxoneflow-resolver-agent/config.template.yaml}
  \item The agent is installed as a \texttt{systemd} service and registered to automatically run at system start.
  \item The non-login user \texttt{resolver} is created and used to execute the \texttt{systemd} service.
  \item The non-login user \texttt{resolver-runtime} is created for use with the optional run-as isolation
    (see \intlink{par:shell-agent-isolation}{Shell Execution Isolation} for this optional configuration).
  \item A default directory for storing secrets is created at \texttt{/var/secrets} with permissions 500.
\end{itemize}

As part of the configuration, a work directory for the resolver will be required.  When this directory
is created, it is recommended to use the owner of \texttt{root:resolver} and permissions of 770.  This
directory will primarily store temporary files used during the execution of \scaresolver.

The default secrets directory \texttt{/var/secrets} is created with ownership \texttt{resolver:resolver} and
permissions 500.  For secret files placed in this directory, it is recommended to each file is owned
by \texttt{resolver:resolver} with permissions of 400.  The permission of 400 will prevent 
build tools from reading the secrets when using the \intlink{par:shell-agent-isolation}{Shell Execution Isolation} option.

\paragraph{Controlling the Distributed Resolver Agent}
\noindent\\The distributed resolver agent runs as a \texttt{systemd} service.  This allows the run status to be controlled
by commands such as "\texttt{systemctl start cxoneflow-resolver-agent}" and\\"\texttt{systemctl stop cxoneflow-resolver-agent}".

The distributed resolver agent runtime logs appear in \texttt{/var/log/syslog}.  To monitor the distributed resolver agent logs, execute the command
\\"\texttt{tail -f /var/log/syslog | grep resolver.agent}".

Debug logging can be turned on for the distributed resolver agent by adding an environment variable in the \texttt{systemd}
service definition.  The following procedure will enable debug logging:

\begin{enumerate}
  \item Edit the file \texttt{/opt/cxoneflow-resolver-agent/cxoneflow-resolver-agent.service}
  \item Add the line "\texttt{Environment=LOG\_LEVEL=DEBUG}" under the existing line starting with\\\texttt{Environment}.
  \item Save the modifications to the \texttt{cxoneflow-resolver-agent.service} file.
  \item Execute the command "\texttt{systemctl daemon-reload}".
  \item Execute the command "\texttt{systemctl restart cxoneflow-resolver-agent}".
\end{enumerate}

\paragraph{Shell Execution}\label{par:agent-shell-execution}

\noindent\\Shell execution of \scaresolver is configured to use an instance of \scaresolver installed on the local system.
The execution of \scaresolverns, along with all build tools it invokes as part of the scan are executed with the \texttt{resolver}
user.  The \texttt{resolver} user is the executing user since the process is spawned from the \texttt{systemd} service that also
runs as the \texttt{resolver} user.

The \texttt{resolver} user is a non-login user that should have no access to do much other than run \texttt{git}, \scaresolverns, and
the build tools invoked as part of the dependency resolution.  The home directory for the \texttt{resolver} user is dynamically set
to the value configured in \intlink{sec:agent-resolver-work-path}{resolver-work-path} when \scaresolver is executed.  The location
of the home directory may have implications for how the build tools run.

Many build tools will have several places where they will look for configurations that are not explicitly placed in the build
definition.  In some cases, the configuration can exist in the home directory of the user running the build tool.  It may be necessary
to replicate build tool settings to the \intlink{sec:agent-resolver-work-path}{resolver-work-path}.  If the build tools use a global location
for the settings, it may be necessary to adjust file/directory permissions to allow the \texttt{resolver} user to access the global
configurations.

The build tools will often use the running user's home directory to write a package cache.  When the tool is invoked,
the running user's home directory is set to the value configured in \intlink{sec:agent-resolver-work-path}{resolver-work-path}.
It may be possible to change the locations where the tools look for configuration or write package caches by configuring the
\intlink{sec:agent-resolver-opts}{resolver-opts} YAML element with
\extlink{https://docs.checkmarx.com/en/34965-132888-checkmarx-sca-resolver-configuration-arguments.html\#UUID-bc93274b-c1c7-ea47-9556-3bd8900711dc_id_CheckmarxSCAResolverConfigurationArguments-CustomParameters}
{custom parameters} passed to the build tools.

If transitioning to a configuration for \intlink{par:shell-agent-isolation}{Shell Execution Isolation}, the contents of the directory
defined in \intlink{sec:agent-resolver-work-path}{resolver-work-path} will be owned by \texttt{resolver:resolver}.  This will likely
cause \scaresolver to fail since the change in configuration will cause the user running the tools to change to
\texttt{resolver-runtime}.  Most of the tools will require files and directories to be owned by\\\texttt{resolver-runtime:resolver}.
It may be necessary to purge the \intlink{sec:agent-resolver-work-path}{resolver-work-path} directory or selectively change
the ownership of build-tool related files/directories to \texttt{resolver-runtime:resolver}.


\subparagraph{Shell Execution Isolation}\label{par:shell-agent-isolation}
\noindent\\Using the shell execution isolation configuration is an advanced option that requires granting limited sudoer privileges
to the \texttt{resolver} user.  The sudoer privileges required are to allow the \texttt{resolver} user to execute \scaresolver
as the user configured in \intlink{sec:agent-resolver-run-as}{resolver-run-as}.  The reason to use this option is to ensure that
the contents of the files located in the \intlink{sec:yaml-secret-root-path}{secret-root-path} can't be read while \scaresolver
is executing.\footnote{This assumes the recommendation of setting the permissions of each file in 
\intlink{sec:yaml-secret-root-path}{secret-root-path} to 400 has been followed.}

The installer creates a no-login user \texttt{resolver-runtime} as a default user that can be referenced in the \intlink{sec:agent-resolver-run-as}{resolver-run-as}
configuration.  Another user can be used as long as the primary group membership is the \texttt{resolver} group.  In most configurations, 
the \texttt{resolver-runtime} user will be sufficient.

The package installer does not configure this user with sudoer privileges by default primarily since the location of the \scaresolver
installation is unknown.  It is also best to allow a system administrator to be explicitly aware of users with sudoer privileges when installing
package.

To enable the \texttt{resolver-runtime} user to have the required privileges, the following procedure can be followed:

\begin{enumerate}
  \item Execute the command "\texttt{visudo /etc/sudoers.d/00-resolver}".
  \item Add the single line:\\"\texttt{resolver ALL=(resolver-runtime) NOPASSWD: SETENV: /path/to/ScaResolver}"
  \item Save the \texttt{/etc/sudoers.d/00-resolver} file.
  \item Configure the element \intlink{sec:agent-resolver-run-as}{resolver-run-as} in \texttt{/etc/cxoneflow-resolver-agent/config.yaml} 
  with the user \texttt{resolver-runtime}.
  \item Restart the \texttt{systemd} service for the distributed resolver agent.
\end{enumerate}

Any configuration for tags that use shell execution of \scaresolver will now run as the user\\\texttt{resolver-runtime}.

\paragraph{Container Execution}
\noindent\\Container execution is supported using the \toolkit build environment that will extend a container image
specified in the \intlink{sec:agent-container-image-tag}{container-image-tag} YAML element.  The extended image
installs \scaresolver at the \texttt{systemd} service start.

The execution of \scaresolver is isolated from the underlying operating system by executing in the container image.
The container image, having all appropriate build tools and build tool configuration, will perform a dependency
tree resolution in the same way as it is done with shell execution.  This is similar to using
\intlink{par:shell-agent-isolation}{Shell Execution Isolation} by delegating execution to the docker image.

Assuming \texttt{docker} is installed, it is generally required to add the \texttt{resolver} user to the \texttt{docker}
group using the command "\texttt{usermod -a -G docker resolver}".  This allows the \texttt{resolver} user to execute
commands to build and run containers.

\subparagraph{Container Execution Security}
\noindent\\The installation of \texttt{docker} is usually done such that the \texttt{docker} daemon runs with
root privileges.  For distributed resolver agent configurations that allow 
\intlink{par:agent-shell-execution}{Shell Execution} along with container execution, this capability could pose
the risk of privilege escalation via the \texttt{docker} runtime.

If not configured for \intlink{par:shell-agent-isolation}{Shell Execution Isolation}, it is possible that
executing build tools via \scaresolver running as the \texttt{resolver} user can escalate privileges
to read and write files with root privileges.  This is due to the \texttt{resolver} user being a member of
the \texttt{docker} group and \scaresolver executing as \texttt{resolver}.  

To avoid the potential for privilege escalation:

\begin{itemize}
  \item Use \intlink{par:shell-agent-isolation}{Shell Execution Isolation} for distributed resolver agents that are configured
    to execute \scaresolver both as a shell execution and using container execution.
  \item If not using \intlink{par:shell-agent-isolation}{Shell Execution Isolation}, install \texttt{docker} in the "rootless"
    configuration.\footnote{As of the writing of this manual, this is not a tested configuration scenario.  It is unknown if rootless will work.
    An alternative would be to avoid configurations that allow both shell and docker execution of \scaresolverns.}
\end{itemize}



\subsection{Distributed Resolver Agent YAML Configuration}

The distributed resolver agent's YAML configuration is deployed after the agent is installed.
Many of the elements share format with the \intlink{sec:yaml-config}{server's configuration elements}. 


Below is an example of a distributed agent YAML configuration.  This example demonstrates:

\begin{itemize}
  \item Secrets are stored in \texttt{/var/secrets}
  \item A common configuration block used by each tag is placed in each tag's configuration using YAML Anchors.
  \item \scaresolver execution uses a work path of \texttt{/var/resolver}.
  \item Shell execution of \scaresolver uses an instance installed at\\\texttt{/opt/resolver/ScaResolver}.
  \item Options for \scaresolver are defined in the \texttt{resolver-opts} element.
  \item All agent tags use the same AMQP configuration via YAML Anchor tags.
  \item The agent tag \texttt{general} is configured to execute \scaresolver as a shell execution.
  \item The agent tag \texttt{java-gradle} executes \scaresolver using a container image \texttt{gradle:8-jdk17-alpine} that
    is then extended by the agent using the \toolkit installed at \texttt{/opt/supply-chain-build-env}.
\end{itemize}

\input{resolver/yaml/example.tex}


\pagebreak

\subsubsection{Distributed Resolver Agent YAML Configuration Tree}\label{sec:agent-yaml-root}

\dirtree{%
    .1 <root>.
    .2 \intlink{sec:yaml-secret-root-path}{secret-root-path}\DTcomment{[Required]}.
    .2 \intlink{sec:agent-serviced-tags}{serviced-tags}\DTcomment{[Required]}.
    .3 \intlink{sec:agent-tag}{<agent tag>}\DTcomment{[At least 1 required]}.
    .4 \intlink{sec:yaml-generic-amqp}{amqp}\DTcomment{[Optional] Default: localhost}.
    .5 \intlink{sec:yaml-generic-amqp-amqp-password}{amqp-password}\DTcomment{[Optional]}.
    .5 \intlink{sec:yaml-generic-amqp-amqp-url}{amqp-url}\DTcomment{[Required]}.
    .5 \intlink{sec:yaml-generic-amqp-amqp-user}{amqp-user}\DTcomment{[Optional]}.
    .5 \intlink{sec:yaml-generic-ssl-verify}{ssl-verify}\DTcomment{[Optional] Default: True}.
    .4 \intlink{sec:agent-public-key}{public-key}\DTcomment{[Required]}.
    .4 \intlink{sec:agent-resolver-opts}{resolver-opts}\DTcomment{[Optional] Default: None}.
    .4 \intlink{sec:agent-resolver-path}{resolver-path}\DTcomment{[Required if not \texttt{run-with-container}]}.
    .4 \intlink{sec:agent-resolver-run-as}{resolver-run-as}\DTcomment{[Optional] Default: run as service user}.
    .4 \intlink{sec:agent-resolver-work-path}{resolver-work-path}\DTcomment{[Optional] Default: /tmp/resolver}.
    .4 \intlink{sec:agent-run-with-container}{run-with-container}\DTcomment{[Required if not \texttt{resolver-path}]}.
    .5 \intlink{sec:agent-container-image-tag}{container-image-tag}\DTcomment{[Required]}.
    .5 \intlink{sec:agent-supply-chain-toolkit-path}{supply-chain-toolkit-path}\DTcomment{[Required]}.
    .5 \intlink{sec:agent-use-running}{use-running-gid}\DTcomment{[Optional] Default: True}.
    .5 \intlink{sec:agent-use-running}{use-running-uid}\DTcomment{[Optional] Default: True}.
}

\input{resolver/yaml/root.tex}
\input{resolver/yaml/serviced-tags.tex}
\input{resolver/yaml/tag.tex}

\subsection{Resolver Configuration Recommendations}

The YAML configuration option \intlink{sec:agent-resolver-opts}{resolver-opts} can be used to provide
configuration options for \scaresolver during execution.  This section discusses recommended
configuration options.

\subsubsection{break-on-manifest-failure}\label{sec:break-manifest}

This is a boolean option that is passed to \scaresolver as the argument \texttt{--break-on-manifest-failure}.  It is recommended
that this is set in the \intlink{sec:agent-resolver-opts}{resolver-opts} configuration.  This will cause any manifest failures
encountered when running \scaresolver to flag the scan with the resolver tag of \textbf{failed}.  If this option is not included,
all scans will have a resolver tag of \textbf{success} regardless of if resoluton of any dependency trees failed when
executing \scaresolverns.

The reason \scaresolver should be configured to run with this option is to make it easy to filter a list of scans by resolver
failure status.  All SCA scans are reported as successfully completed if the dependency tree resolution executes to
any type of completion.  The dependency resolution may completely or partially fail but the scan status will reflect
as a successful scan.  Any partial results will be reported but it requires some manual review of logs to understand if there
were any partial dependency tree resolution failures.

\subsubsection{scan-containers}
This is a boolean option that is passed to \scaresolver as the argument \texttt{--scan-containers}.  It is recommended that
this option is \textbf{not} set in the \intlink{sec:agent-resolver-opts}{resolver-opts} configuration.

There are a few reasons for omitting this flag; the main reason is that container security scans have moved away from
using \scaresolver to perform the scan.  Container security scans are now an independent scan option and no longer
report results provided by \scaresolver when used by \cxonens.  This option may remain in \scaresolver for backwards
compatibility with other Checkmarx products.

\subsection{Limitations}
Please note the following limitations apply when using the distributed resolver agent:

\begin{itemize}
  \item Server-side configurations with \texttt{clone-auth} using SSH keys will fail.
  \item Windows base container images can not be used to run \scaresolver in a container.  Only Linux base images are supported.
  \item The Containter Security scans recently moved away from using \scaresolverns, thus container scans will currently
    execute in the \cxoneflow server side environment.
\end{itemize}

